\documentclass[SRC.tex]{subfiles}


\begin{document}
	​American Farm Bureau. (n.d.). Where does energy come from? Retrieved from American farm bureau foundation for agriculture: \newline \url{https://www.agfoundation.org/common-questions/view/Where-does-energy-come-from}
	
	Dilallo, M. (n.d.). The world has 53.3 years of oil left. Retrieved from USA TODAY: \url{https://eu.usatoday.com/story/money/business/2014/06/28/the-world-was-533-years-of-oil-left/11528999/}
	
	DrivKraftDanmark. (2019). Energistatistik 2019. DrivKraftDanmark. 
	
	Gate21. (n.d.). Grøn omstilling i 2030. Retrieved from Gate21: \url{https://www.gate21.dk/groen-omstilling-i-2030/}
	
	Granados, F. (2014). Thermal model of the EuroDish Solar Stirling Engine.  
	
	Haywood, D. (n.d.). AN INTRODUCTION TO STIRLING-CYCLE MACHINES.  
	
	Holck, P., og Kraaer, J. (2009). Orbit A. Systime. 
	
	promes. (n.d.). EURODISH SYSTEM. Retrieved from promes: \url{https://www.promes.cnrs.fr/index.php?page=eurodish-system#prettyPhoto}
	
	Ritzau. (2019, december 20). Nye rekorder for grøn energi i Danmark. Retrieved from energiwatch: \url{https://energiwatch.dk/Energinyt/PolitikMarkeder/article11839395.ece}
	
	Schiel, W., og Laing, D. (2015). Survey on Solar-Electric Dish/Stirling Technology.  
	
	SOLO Stirling. (n.d.). Fact sheet: SOLO Stirling 161. Retrieved from Buildup: \newline 
	\url{https://www.buildup.eu/en/practices/cases/solo-stirling-161-fact-sheet-germany} 
	
	Systime. (n.d.). Orbit A HTX. Systime. 
	
	Vourvoulias, A. (2021, februar 16). How Efficient Are Solar Panels? Retrieved from Greenmatch: \url{https://www.greenmatch.co.uk/blog/2014/11/how-efficient-are-solar-panels} 
	
	Wikipedia. (n.d.). Parisaftalen (2015). Retrieved from Wikipedia: \newline \url{https://da.wikipedia.org/wiki/Parisaftalen(2015)} 
	
	Wikipedia. (n.d.). Stirling Engine. Retrieved from Wikipedia: \url{https://en.wikipedia.org/wiki/Stirling_engine#/media/File:Stirling_Cycle_color.svg}
\end{document}